Proposed Solution

### 2016-01-29 intro1.tex
autocommit

From a  practical perspective there is no additional burden 
to the users: they can simply use \app to check for errors in their configuration files. However, they can also easily extend the framework themselves. The system is designed to be highly modular. If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class. The new learner can be added to \app and this way it can check additionally a new set of errors.

>>>>

From a practical perspective \app introduces no additional burden 
to the users: they can simply use \app to check for errors in their configuration files. However, they can also easily extend the framework themselves. The system is designed to be highly modular. If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class. The new learner can be added to \app and this way it can check additionally a new set of errors.
